{\fontfamily{ptm}\selectfont Reading Notes}

### 2025-03-27 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, changes

\begin{abstract} 
    Reports on papers read. 
    This is a LaTEX file for my own notes taking. 
    It may accelerate the process of writing my thesis for my PhD degree. 
    \todo{
        This is just pseudo text. This is just pseudo text. 
        This is just pseudo text. This is just pseudo text \cite{necoara_linear_2019}. 
    }
    \todoinline{This paper is currently in draft mode. Check source to change options. }
\end{abstract}
\chapter{The Basics of Optimization Theories}

@@

            A few more words are needed before the theorem for the Error bound conditions and the quadratic growth condition.

>>>>

\begin{abstract} 
    Reports on papers read. 
    This is a LaTEX file for my own notes taking. 
    It may accelerate the process of writing my thesis for my PhD degree. 
    \todo{
        This is just pseudo text. This is just pseudo text. 
        This is just pseudo text. This is just pseudo text \cite{necoara_linear_2019}. 
    }
    \todoinline{This paper is currently in draft mode. Check source to change options. }
\end{abstract}
\chapter{The Basics of Optimization Theories}
    Notations in this chapter are not shared and they are for this chapter only.

@@

            The following theorems are about the relation between EB and QFG.
